Intrusion Detection with Genetic Algorithms and Fuzzy Logic

### 2013-10-15 paper.tex
Put two algorithms into paper, also moved some sections around.

\documentclass{sig-alternate}
\usepackage{color}

@@

\subsection{Algorithm Overview}
The algorithm that is used in~\cite{6496342, 6559603} first randomly finds a rule. Then the rule is improved in the training phase. After that, the rules are used to classify the data into classes in the testing phase. The pseudo code below describes the fuzzy genetic algorithm that is used.

for each record

   for each rule

      for each attribute

         prob = fuzzy();

         totalprob = totalprob + prob;

      If (totalprob > threshold)

         class is attack;

         class is normal;

      compare the predicted result with actual result

\mycomment{put in alpha and beta symbols}

      find A, B, alpha, and beta,

   calculate fitness

   // create next generation

   preserve\_best()

   crossover()

   mutation()

// A is total number of attack records. B is total number of normal records. alpha is total number of attack records correctly identified as attack. beta is total number of normal records incorrectly classified as attack (false positive).

@@

In order to measure the probability of an attack, a trapezoidal shape was used in the algorithm. The trapezoidal shape has four parameters: a, b, c, and d. The following algorithm calculates the probability of being attacked:

if (data value is between b and c)

   prob =1.0

else if (data value is between a and b)
\begin{equation*}
   prob = \frac{data - a}{b-a}
\end{equation*}

else if (data value is between c and d)
\begin{equation*}
   prob = \frac{d-data}{d-c}
\end{equation*}

   prob = 0.0

\mycomment{Put in trapezoidal shape figure.}

>>>>

\documentclass{sig-alternate}
\usepackage{color}
\usepackage{algorithmic}
\usepackage{algorithm}

@@

\subsection{Fuzzy Algorithm}
In order to measure the probability of an attack, a trapezoidal shape was used in the algorithm. The trapezoidal shape has four parameters: a, b, c, and d. 
\mycomment{Put in trapezoidal shape figure.} Algorithm~\ref{alg:fuzAlg} calculates the probability of being attacked.

\begin{algorithm}
\caption{Fuzzy Algorithm}
\label{alg:fuzAlg}
\begin{algorithmic}
\IF{data value is between b and c}
  \STATE{prob = 1.0}
\ELSIF{data value is between a and b}
  \STATE{
    prob = $(\textrm{data}-a)/(b-a)$
  }
\ELSIF{data value is between c and d}
  \STATE{
    prob = $(d-\textrm{data})/(d-c)$
  }
\ELSE \STATE{prob = 0.0}
\ENDIF
\end{algorithmic}
\end{algorithm}

\subsection{Algorithm Overview}
The algorithm that is used in~\cite{6496342, 6559603} first randomly finds a rule. Then the rule is improved in the training phase. After that, the rules are used to classify the data into classes in the testing phase. Algorithm~\ref{alg:fuzGenAlg} describes the fuzzy genetic algorithm that is used.

\begin{algorithm}
\caption{Fuzzy Genetic Algorithm}
\label{alg:fuzGenAlg}
\begin{algorithmic}
\FOR{each record}

  \FOR{each rule}
    \FOR{each attribute}
      \STATE{prob = fuzzy();}
      \STATE{totalprob = totalprob + prob;}
    \ENDFOR

    \IF{totalprob > threshold} 
      \STATE{class is attack;}
      \ELSE \STATE{class is normal;}
    \ENDIF
  \ENDFOR

  \STATE{compare the predicted result with actual result}
  \STATE{find A, B, $\alpha$, and $\beta$}
  \STATE{// A is total number of attack records. B is total number of normal records. $\alpha$ is total number of attack records correctly identified as attack. $\beta$ is total number of normal records incorrectly classified as attack.}
\ENDFOR
\STATE{calculate fitness}
\STATE{//create next generation}
\STATE{preserve\_best()}
\STATE{crossover()}
\STATE{mutation()}
\end{algorithmic}
\end{algorithm}

@@
